method

### 2021-11-16 06_Paper/ER-ED/method.Rmd
added data frame

# new empty frame to store files into
data_ER = data.frame(ID = character(), )

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
```

>>>>

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())

# store arousal and effort ratings in data_ER frame

for (i in 1:length(datalist_ER)) {

  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["instr_1"]],datalist_ER[[i]][["slider_arousal.response"]],datalist_ER[[i]][["slider_effort.response"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)),]

  data_ER = rbind(tmp, data_ER)

}

```
